---
title: "Creating the ``r params$package_name`` R package"
author: "Mohit Saini"
date: "01/18/2023"
knit: litr::render
output: litr::litr_html_document
params:
  package_name: "shinydrawer" # <-- change this to your package name
  package_parent_dir: "." # <-- relative to this file's location
---

<!-- This Rmd file contains all the code needed to define an R package.  Press "Knit" in RStudio or more generally run `litr::render("name-of-this-file.Rmd")` to generate the R package.  Remember that when you want to modify anything about the R package, you should modify this document rather than the package that is outputted.
-->

## Package setup

We start by specifying the information needed in the DESCRIPTION file of the R package.

```{r package-setup, message=FALSE, results='hide'}
usethis::create_package(
  path = ".",
  fields = list(
    Package = params$package_name,
    Version = "0.0.0.1",
    Title = "A Package That contains a shinydrawer function code.",
    Description = "This package code for the shinydrawer function as per the test case.",
    `Authors@R` = person(
      given = "Mohit",
      family = "Saini",
      email = "msaini0r@gmail.com",
      role = c("aut", "cre")
      )
  )
)
usethis::use_mit_license(copyright_holder = "Mohit. Saini")
```

## Now to the package itself

### Define a function

Let's define a function for our R package:

```{r}
#'

shinydrawr <- function(){
    
    line_data <- linear_data() %>%
        filter(data == "line_data")
    
    point_data <- linear_data() %>%
        filter(data == "point_data")
    
    data <- list(line_data = line_data, point_data = point_data)
    
    drawr(data              = data,
          aspect_ratio      = 1,
          linear            = "true",
          free_draw         = TRUE,
          points            = "full",
          x_by              = 0.25,
          draw_start        = 1,
          points_end        = 20,
          show_finished     = T,
          shiny_message_loc = message_loc,
          x_range           = linear_x_range(),
          y_range           = linear_y_range()
    )
    
}
```

Code chunks whose first line starts with `#'` are added to the package.

We can try running it.

## Documenting the package and building

We finish by running commands that will document, build, and install the package.  It may also be a good idea to check the package from within this file.

```{r}
litr::document() # <-- use instead of devtools::document()
# devtools::build()
# devtools::install()
# devtools::check(document = FALSE)
```


